---
output: 
  revealjs::revealjs_presentation:
    keep_md: True
    transition: zoom
    self_contained: false
    reveal_plugins: notes
    css: styles.css
    center: true
    mathjax: NULL
---
<style>
p {
    color:red;
}
</style>

# {#title data-background="https://www.gradedtalon.com/wp-content/uploads/2021/05/1610520139_T1H1DR_Stock_Market-1.jpg"}


<h1 style="color: #fff">Pairs Trading</h1>
<h3 style="color: #fff">Logan Morrill</h3>

```{r echo = FALSE}
knitr::opts_chunk$set(warning = FALSE)
#Packages
pacman::p_load(tidyverse,dygraphs,lubridate,tidyquant,timetk, ggpubr,plotly)
```
# {data-background=#262626}
<h1 style="color: #fff">What is Pairs Trading?</h1>

<p>Strategy: Trade 2 stocks betting they will revert back the mean of the spread between their prices <br>
Stock Picks: Historically Highly correlated stocks <br>
Correlation: >= 80 <br>
When to Trade: Spread passes 1 std dev up or down <br>
How to Trade: Go long the underperforming security and sell short the outperforming security</p>

```{r Stock 1 Year Comparison Function, echo=FALSE}
#Stock 1 Year Comparison Function
#If cor is entered will return the correlation %
#If dif is entered will return a graph of the difference between the stock prices with mean and st_dev
#Else return a chart of the stock prices
stonk_calculator <- function(tickers,x) { #Get price data for 1 year
  stonks <- tq_get(tickers, get = "stock.prices", from = today() - years(1), to = today())
  closes <- stonks %>% #get close prices side by side
    select(date,symbol,close) %>%
    pivot_wider(names_from = symbol, values_from = close)
  if (x == 'cor') { #find correlation between tickers
    res <- cor.test(closes[[2]], closes[[3]], method = "pearson")
    paste(colnames(closes)[2],colnames(closes)[3],'correlation:',round(res$estimate * 100,3))
  } else if (x == 'dif') {
    closes$dif <- closes[[2]] - closes[[3]] #create difference between prices
    closes$mean <- mean(closes$dif) #create mean
    closes$up_std_dev <- closes$mean + sd(closes$dif) #create upper std_dev
    closes$down_std_dev <- closes$mean - sd(closes$dif) #create lower std_dev
    #Create ticker price difference chart
    dif <- ggplot(data = closes, aes(x = date, y = dif)) +
      geom_point(size = .01, aes(text = paste(colnames(closes)[2],closes[[2]],'\n',colnames(closes)[3],closes[[3]]))) + #add stock prices
      geom_line() +
      geom_hline(yintercept = closes$mean, color = 'red', size = .25) + #add horizontal mean line
      geom_hline(yintercept = closes$up_std_dev, color = 'red', linetype = 'dotted', size = 0.1) + #add horizontal upper std_dev line
      geom_hline(yintercept = closes$down_std_dev, color = 'red', linetype = 'dotted', size = 0.1) + #add horizontal lower std_dev line
      labs(x = '', y = '', title = paste(colnames(closes)[2],'and',colnames(closes)[3],'stock price spread')) + #make title tickers
      theme_bw()
    ggplotly(dif)
  } else {#Create chart of ticker prices for 1 year
    stonks_chart <- stonks %>%
      select(symbol, date, close) %>%
      pivot_wider(names_from = symbol, values_from = close) %>%
      tk_xts(date_var = date)
    dygraph(stonks_chart)
  }
}
```

# General Motors (GM) and Ford (F)
```{r GM_F_Pair, echo=FALSE} 
#Compare Stock Returns for General Motors (GM) and Ford (F) to find a pair
GM_F <- c('GM','F')
stonk_calculator(GM_F,'cor')
#Correlation = 73.195
stonk_calculator(GM_F,'chart')
```
## {data-background=#262626}
<h2 style="color: #fff">Mean reverse plot</h2>
```{r GM_F_Difference, echo=FALSE}
stonk_calculator(GM_F,'dif')
```
## {data-background=#262626}
<h2 style="color: #fff">Is GM and F a good pair?</h2>

<p> GM and F pair is risky, but could be traded </p>

# Gold (GLD) and Silver (SLV)
```{r GLD_SLV_Pair, echo=FALSE} 
#Compare ETF Returns for Gold (GLD) and Silver (SLV) to find a pair
GLD_SLV <- c('GLD','SLV')
stonk_calculator(GLD_SLV,'cor')
#Correlation = 46.912
stonk_calculator(GLD_SLV,'chart')
```

## {data-background=#262626}
<h2 style="color: #fff">Is GLD and SLV a good pair?</h2>

<p> GLD and SLV pair is extremely risky, not suitable for trading </p>

# S & P (SPY) and Nasdaq (QQQ)
```{r SPY_QQQ_Pair, echo=FALSE} 
#Compare ETF Returns for S & P (SPY) and Nasdaq (QQQ) to find a pair
SPY_QQQ <- c('SPY','QQQ')
stonk_calculator(SPY_QQQ,'cor')
#Correlation = 96.025
stonk_calculator(SPY_QQQ,'chart')
```
## {data-background=#262626}
<h2 style="color: #fff">Mean reverse plot</h2>
```{r SPY_QQQ_Difference, echo=FALSE}
stonk_calculator(SPY_QQQ,'dif')
```
## {data-background=#262626}
<h2 style="color: #fff">Is SPY and QQQ a good pair?</h2>

<p> SPY and QQQ pair has little risk, very suitable for trading </p>

# {data-background=#262626}
<h1 style="color: #fff">Trade Pair Conclusions</h2>

<h2 style = "color:red"> SPY and QQQ: Yes <br>
GLD and SLV: No <br>
GM and F: depends on risk tolerance
</h2>